FIXME

### 2013-09-17 writeups/proposal/proposal.tex
finished first draft
Former-commit-id: 0a609af09e5fbe0f9599cfde80a42e14214f1a5c [formerly 0e1d88f08804768b596525c983820f3d1c2d0ce4]
Former-commit-id: e0ea74523114417ca1d0541080dd6ed9353be3ca

\subsubsection{StackOverflow Dataset Modifications}

@@

\subsubsection{Analyze Recency for User-Generated Hashtags}

@@

\subsubsection{Incorporating Recency Into Random Permutations}

@@

\subsubsection{Incorporating Word Order Into ACT-R}

@@

\subsubsection{Top Hashtag Prediction}

TODO: vector-based and act-r head to head on twitter common-hashtags
TODO: head to head without word order on twitter common-hashtags
TODO: head to head on stackoverflow

TODO: head to head on twitter popular-users dataset
TODO: head to head on stackoverflow

>>>>

Each proposed experiment aims to answer a specific research question in this study.
The results from Experiment 1 will show how a user's prior hashtag use influences their likelihood of using that hashtag in the future, and test whether the observed data fit the ACT-R frequency/recency decay rate theory.
The output from Experiment 1 will be a model of how a user's prior hashtag use influences the probability of using that hashtag in the future for both the Twitter and StackOverflow datasets.
Experiment 2 will use the results from Experiment 1 and develop the best method to incorporate user's past tagging history in the random-permutations model, where user history is currently not being used.
Experiment 3 will explore various methods for incorporating word order information into the ACT-R Bayesian model, where this information is currently not being used.
The outputs of Experiment 2 and 3 are improved ACT-R and random-permutation models that have properly incorporated the strengths of each other: word-order strength from random permutations and user history from ACT-R.
Finally, Experiments 4 and 5 will directly compare model accuracy between the two models and evaluate overall performance.
Experiment 4 is focused primarily on hashtag prediction when no user prior history is available, while Experiment 5 will test how much performance improves when that history is available.

\subsubsection{Preparation Experiment: StackOverflow Dataset Modifications}

@@

\subsubsection{Experiment 1: Analyze Recency for User-Generated Hashtags}

@@

\subsubsection{Experiment 2: Incorporating Recency Into Random Permutations}

@@

\subsubsection{Experiment 3: Incorporating Word Order Into ACT-R}

@@

\subsubsection{Experiment 4: Top Hashtag Prediction}

After incorporating the relative strengths of each model into the other, the accuracy of the two models will be compared directly.
Both models will be evaluated on predicting hashtags for tweets in the popular-hashtags dataset and predicting tags for posts on StackOverflow.
However, the user prior hashtag use will not be available for the popular-hashtags dataset, since this subset was collected across the entire twitter user population.

\subsubsection{Experiment 5: User-Customized Hashtag Prediction}

In order to directly cmopare performance differences for each model when generating user-customized tag predictions, the models will be tested on the StackOverflow dataset and the Twitter popular-users dataset.
Each dataset contains the entire tag history of either all users (StackOverflow) or the most popular users (Twitter).
The main evaluation will be the amount of performance gain achieved when the models generate tags that are based on past user behavior compared to models that generate tags that are bases purely on context.

\subsection{Summary}

The end result of this research will be a better understanding of how a user's past tagging history influences future tag use,
as well as two cognitively-plausible models for making user-customized tag predictions for StackOverflow posts and Twitter tweets. 
Overall performance differences between an ACT-R's Bayesian retrieval model and a random-permutation vector-based model will be directly compared.
Improvements made in each model in order to increase performance at this tagging task may suggest model modifications that could be made to improve model performance for other tasks.
Further, these improvements may uncover model modifications that could improve model fit across all tasks (i.e., suggest cognitive architectural modifications).
In addition, if model accuracy is high enough, then these developed models may be applied to general tag recommendation systems for either Twitter or StackOverflow,
and possibly for other sites where users generate and tag content.
